Stable Hot Spot Analysis (Draft)

### 2017-06-12 paper-main.tex
raw idea of intro and related work

For urban city planers, the detection of Intra Urban Heat Islands (IUHI) is of
high interest as high temperatures impact energy
consumption~\cite{Hassid.2001.Electricity_UHI} as well as human
health~\cite{Ye.2012}. The effect that the temperatures between an urban area
and its surroundings differ, called the Urban Heat Island effect
\cite{Oke1982energetic}, has long been the subject of research. Most historical
studies conducted had to rely on few, fixed weather stations, low
spatio-temporal resolution of satellites or small-scale mobile measurements by
car, preventing the modelling of finer-grained temperature differences within an
urban area itself. With the advent of inexpensive mobile sensors, higher
spatio-temporal resolution of satellites and volunteered geographic
informations, to name just a small selection, it is now feasible to focus on the
temperature differences in a city as the subject of interest.

Hot spot analysis is a tool which is suited to detect such areas. In the context
of IUHI we can detect those areas where the temperature is significantly
different from the mean temperature of our study area. This enables us to
identify points of interest without the need to pre-process the data.

Although existing methods are independent of concrete values, their results are
highly dependent on the size of the study area and their parametrization such as
the weight matrix in the case of the Getis-Ord statistic. This dependency can
lead to unstable hot spots, where the identified hot spots only appear in one 
specific combination of parameter. The generalization of insights gained from
unstable hot spots is suboptimal. A city planer who has to rely on those
insights will most likely prioritize the wrong area to invest his limited
resources. Given the increasing importance to detect extreme local temperatures
in cites, see e.g. \cite{Hansen.2010, GRL:GRL22143, department2014world}, means
to reliably detect and mitigate the effect of temperature extremes in a
proactive fashion are needed.

To solve this problem, we first propose a metric to measure the stability of a
hot spot analysis regarding its parametrization of the weight matrix called the
\emph{Stability of Hot spot} (SoH). This metric measures whether a hot spot
found for a given weight matrix is carried over to the found hot spots with a
different weight matrix. This enables us to quantify the stability of any hot
spot analysis. Based on our reasoning behind the instability of existing hot
spot analyses, we propose a modification of the well known Getis-Ord statistic
($G^*$): the \emph{Focal Getis-Ord} statistic (Focal $G^*$). Instead of the
global mean and variance used by $G^*$, it only uses the mean and variance of a
predefined region around each point. This region is a subset of the whole study
area. By doing this, the instability is contained within a smaller region and
thereby independent of the parametrization of the weight matrix. We test our
stability metric as well as this modified approach on data given by two
temperature snapshots of the city of Karlsruhe taken in 2008.

@@

\subsection{Urban Heat Island}

The scientific interest in the phenomena of UHI is well established. One of the
earliest known overviews of the scientific literature of the city climates is
given by Albert Kratzer 1937~\cite{dieckmann1938stadtklima}. At that time
already, relations between temperature, humidity, human heat fluxes and air
pollution are investigated.

A more recent overview comes from Arnfied~\cite{Arnfield.2003}. The focus here
lies on the development in the field of climatology between 1980 and 2003. In
particular, the rise of simulations and modelling is lauded, but, to quote
Arnfield, ``simple methods are still needed to estimate UHI intensity within
urban areas''~\cite{Arnfield.2003}.

Schwarz~et~al.~\cite{Schwarz.2011} compare 11 different Surface Urban Heat
Island (SUHI) indicators on a dataset of 263 European cities with monthly mean
temperatures. They show that the selection of indicators is important for the
detection of UHI due to possible instabilities of each indicator.

A more recent development is the focus on IUHI. The definition for IUHI comes
from Martin et al.~\cite{Martin.2015}. By defining thresholds with respect to
spatial reference, these enable the detection of hot spots in a city, which
Martin et al. call surface intra-UHI. This boils down to five steps, i.e.
essentially a comparison of absolute deviation from the mean temperature given a
survey area. The results can then be used to detect areas of interest in a city
and potentially trigger alerts for a much finer spatial granularity.

While the proposition to examine urban micro-climates can be traced back as far
as 1937~\cite{dieckmann1938stadtklima}, we have found only few works in this
field. Schwarz et al.~\cite{Schwarz.2012} state that the reduction of an UHI to
a single value for a whole city is questionable regarding its explanatory power.
But also that there is currently no other way to quantify the differences
amongst cities.

The difficulties presented by comparing the UHI values between different cities
are the topic of Stewart and Oke~\cite{Stewart2012}. They propose the use of
local climate zones (LCZ) to standardise the methodology and terminology.

Another area where urbanizations affects the temperature distribution are
subsurface temperatures. Menberg et al.~\cite{Menberg.2013} look into the
distribution of the temperatures below the surface -- the subsurface
temperature. They find local hot spots of heat with deviations of up to
+20\textdegree{K} in some areas related to local heat sources.

\subsection{Hot Spot Analysis}

>>>>

\begin{itemize}
\item hot spot analysis is important
\item similar to cluster analysis
\item is important to identify interesting areas 
\item typical problem is the correct detection method and parametrization
\item inital work of bruns and viliam 2017 show the instability and present simple metric and stable  method
\item here, we build upon that work and examine in more detail the impact of the different parameter with the standard $G^*$ and focal $G^*$, in particular the size of the study area (focal matrix), the detail of the resolution (zoom) and the size of the neighbourhood (weight matrix)
\item in particular, we compare the stability for all possible combinations and isolate the effect of single parameter by clever aggregation
\item We test on well-known taxi data set for easy comparison and so that in can be easily replicated
\end{itemize}

@@

\begin{itemize}
\item goal Here: some cluster analysis
\item typical clustering apporaches -> phd symposium as examples
\end{itemize}
